Modeling defoliation as a proxy for tree health: A case study using machine-learning and hyperspectral remote sensing data

### 2019-06-09 analysis/paper/Schratz_hyperspectral.tex
restructure ToC
add refs to introduction

% Explain how remote sensing is used in forestry (potential to map forest health)
% Link remote sensing and machine-learning
The use of machine-learning algorithms for analyzing remote sensing data has seen a huge increase in the last decade.
Ever since the launch of the first Sentinel satellite in 2014 the amount of freely available imagery data has increased enormously (REF).
At the same time, the implementation of algorithms (both statistical and machine-learning) has been greatly simplified in the open-source community.
Scientists can nowadays relively easily feed large amounts of data into complex algorithms in a semi-automated way.
These facts combined with a high temporal and spatial coverage of input data enable the possibility to analyze temporal changes of the environment on a large scale.

% link to forest health analysis and show exemplary studies
The monitoring of forest ecosystems is one exemplary field that profits from these new possibilities.
Specifically the monitoring of forest health got simplified with the ability of analyzing large scale data in efficient algorithms that are able to predict to unknown areas.
For this task, usually optical data from multi-/hyperspectral satellites is used.
Various indices are calculated from the data with the aim of carrying out temporal change detections \citep{zhang2016} or analyses about the forest health status for a specific date \citep{townsend2012}.
% TODO: check if refs match context
Vegetation indices have shown the potential to provide valuable information for analyzing triggers to forest health \citep{jiang2014, adamczyk2015}.
More and more studies focus on using machine-learning algorithms such as \ac{RF} \citep{belgiu2016, lary2016, michez2016}.
Overall, the idea is to fit a robust model which can be used to make predictions to (large) unknown areas, providing valuable information about the health condition of forest stands without the need for ground-truth data in these regions.

@@

@@

\subsubsection{Feature sets}

@@

\subsection{RMSE vs. plot characteristics}

@@

\subsection{Variable importance}

\subsection{Spatial prediction}

\subsection{Comparison to other studies}

@@

\section{Conclusion}

>>>>

% Explain how remote sensing is used in forestry (potential to map forest health)
% Link remote sensing and machine-learning
The use of machine-learning algorithms for analyzing remote sensing data has seen a huge increase in the last decade \citep{lary2016}.
Especially since the launch of the first Sentinel satellite in 2014 the amount of freely available imagery data has increased greatly.
At the same time, the implementation and usability of algorithms (both statistical and machine-learning) has been greatly simplified in the open-source community.
Scientists can nowadays relatively easily feed large amounts of information into complex models in a semi-automated way.
These points enable the possibility to analyze (temporal) changes of the environment on a large scale \citep{ma2015}.

% link to forest health analysis and show exemplary studies
The monitoring of forest ecosystems is one exemplary field that profits from these new possibilities.
Specifically the monitoring of forest health profited from the ability of analyzing large scale data with efficient algorithms able to predict to unknown areas \citep{hawrylo2018, mascaro2014}.
For this task, usually optical data from multi-/hyperspectral satellites is used.
Various indices are calculated from the data with the aim of carrying out temporal change detections \citep{zhang2016} or conduct analyses about the current health status \citep{townsend2012}.
Vegetation indices have shown the potential to provide valuable information for analyzing triggers to forest health \citep{jiang2014, adamczyk2015}.
Most studies focus on applying the Random Forest algorithm \ac{RF} \citep{belgiu2016, lary2016, michez2016}.
Others are only used in few studies such as Support Vector Machines \citep{clark2018} or deep-learning algorithms such as Artifical Neural Networks \citep{ingram2005, rocha2018}.
Overall, the idea is to fit a robust model which can be used to make predictions to (large) unknown areas, providing valuable information about the health condition of forest stands without the need for ground-truth data in these regions.

@@

\subsection{Exploratory data analysis}
% TODO: Explain why this is necessary here (differentes between plots)

@@

\subsubsection{Feature sets}
% TODO: talk about the reasons behind different features sets: environmental implications

@@

\subsection{Performance vs. plot characteristics}

@@

\subsection{Feature selection methods}

\subsection{Comparison to other studies}
% TODO: Mention that (probably) most environmental studies only use PCA
% TODO: find studies comparing filter methods
% TODO: Find studies tackling the case of defoliation

@@

\section{Outlook and conclusion}
